**Machine learning classification by fitting amplicon sequences to existing OTUs**

### 2023-07-05 submission/second_revision/manuscript.Rmd
fix citation error
update repo link

**Code Availability.** The analysis workflow was implemented in
Snakemake @koster2012. Scripts for analysis were written in R @R2020 and
GNU bash @GNUbash. The software used includes mothur v1.47.0
@schloss2009, VSEARCH v2.15.2 @rognes2016, RStudio @RStudio2019, the
Tidyverse metapackage @wickham2019, R Markdown @xie_r_2018, the SRA
toolkit @noauthor_sra-tools_nodate, and conda @noauthor_anaconda_2016.
The complete workflow and supporting files required to reproduce this
study are available at:
<https://github.com/SchlossLab/Armour_OptiFitGLNE_XXXX_2023>

>>>>

**Code Availability.** The analysis workflow was implemented in
Snakemake @koster2012. Scripts for analysis were written in R @R2020 and
GNU bash @GNUbash. The software used includes mothur v1.47.0
@schloss2009, VSEARCH v2.15.2 @rognes2016, RStudio @RStudio2019, the
Tidyverse metapackage @wickham2019, R Markdown @xie_r_2018, the SRA
toolkit @noauthor_sra-tools_nodate, and conda @noauthor_anaconda_2016.
The complete workflow and supporting files required to reproduce this
study are available at: [https://github.com/SchlossLab/Armour_OptiFitGLNE_mSphere_2023](https://github.com/SchlossLab/Armour_OptiFitGLNE_mSphere_2023)
